---
title: "Appendix of final assessment"
author: "YUE LI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. Dataset

### 1.1 Basemap of London

1. Go to  [OSM-GB-England](http://download.geofabrik.de/europe/great-britain/england.html) website;

2. Scroll down to look for Greater London and download the corresponding [.shp.zip](http://download.geofabrik.de/europe/great-britain/england/greater-london-latest-free.shp.zip) file;

3. The right name of the file is 'statistical-gis-boundaries-london.zip';

4. Unzip the data and save it.


### 1.2 London Gender Pay Gap Dataset

1. Go to [ONS](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/datasets/annualsurveyofhoursandearningsashegenderpaygaptables) website;

2. Navigate to '2019 updated revised edition of this dataset' and download it;

3. The correct downloaded file name should be 'genderpaygap2019revised.zip';

4. Unzip and save it.


### 1.3 Datasets for calculating Fairness Index

#### 1.3.1 

#### 1.3.2


### 1.4 File checklist

Original dataset                     | Sub file needed
---                                  | ---
statistical-gis-boundaries-london.zip| London_Borough_Excluding_MHW.shp
genderpaygap2019revised.zip          | Table 7.12 - Work Geography Table 7.12  Gender pay gap 2019.xls

---

## 2. Load packages

There are all the packages needed for running this markdown file. To make things tidy, I choose to mute all the messages following this chunk.
```{r, message=FALSE}
library(sf)
library(tmap)
library(tmaptools)
library(tidyverse)
library(here)
library(readxl)
library(RSQLite)
library(dplyr)
```


## 3. Plots for Gender Pay Gap

### 3.1 Map

```{r}
#Set work directory
setwd('~/Documents/CASA/CASA0005-GIS/gis-coursework')

#Read the shp file
Londonborough <- st_read("statistical-gis-boundaries-london/ESRI/London_Borough_Excluding_MHW.shp")%>%
  st_transform(., 27700) 

#Read the Gender Pay Gap file 
#Only extract the data of each borough of Greater London
#Do not keep the column of the median value
GenderPayGap <- read_excel("genderpaygap2019revised/Table 7.12 - Work Geography Table 7.12  Gender pay gap 2019.xls", sheet = "All")%>% 
  .[c(226:239,241:259),c(1,2,4)]

#For simply use, rename the columns and round the figures
names(GenderPayGap) <- c('Borough','GSS_CODE','GPG-Mean')

GenderPayGap$`GPG-Mean` <- as.numeric(GenderPayGap$`GPG-Mean`)
```


```{r}
#Use the same GSS code to collaborate two datasets
data1 <- merge(Londonborough, GenderPayGap, by='GSS_CODE')

#It just a preview
#The complete map would be shown in section 6

## tmap_mode("view") #interactive map
tmap_mode('plot') #normal map

breaks = c(-10, 0, 10, 15, 20) 

tm1 <- tm_shape(data1) + 
  tm_polygons(col = "GPG-Mean", 
              title = 'Mean of Gender Pay Gap',
              legend.hist = TRUE)+
  tm_layout(legend.outside = TRUE)+
  tm_borders()
#for interactive map, do not forget +
#  tm_basemap(server="OpenStreetMap",alpha=0.5)

tm1

tmap_save(tm=tm1,filename = 'GenderPayMap.png')
```

### 3.2 Other plots

## 4. Calculation of the Fairness Index

## 5. Plots for the Fairness Index

### 5.1 Map

### 5.2 Other plots


## 6. Map Collabration
'tmap' sth.
think about the **Legend** and **Scale level**
```{}
tmap_mode("plot")

# set the breaks
# for our mapped data
breaks = c(0, 5, 12, 26, 57, 286) 

# plot each map
tm1 <- tm_shape(Hotels) + 
  tm_polygons("Accomodation count", 
              breaks=breaks,
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(a)", position=c(0,0.85), size=1.5)

tm2 <- tm_shape(Airbnb) + 
  tm_polygons("Accomodation count",
              breaks=breaks, 
              palette="PuBu") + 
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(b)", position=c(0,0.85), size=1.5)

tm3 <- tm_shape(UK_outlinecrop)+ 
  tm_polygons(col="darkslategray1")+
  tm_layout(frame=FALSE)+
  tm_shape(Worldcities2) +
  tm_symbols(col = "red", scale = .5)+
  tm_text("CITY_NAME", xmod=-1, ymod=-0.5)

legend <- tm_shape(Hotels) +
    tm_polygons("Accomodation count",
                palette="PuBu") +
    tm_scale_bar(position=c(0.2,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.65,0.6))+
    tm_layout(legend.only = TRUE, legend.position=c(0.2,0.25),asp=0.1)+
    tm_credits("(c) OpenStreetMap contrbutors and Air b n b", position=c(0.0,0.0))
  
t=tmap_arrange(tm1, tm2, tm3, legend, ncol=2)

t
```


## 7. Comparison Plots
histogram???
line graph??


## 8. INDEX

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


