---
title: "Appendix of final assessment"
author: "YUE LI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. Dataset

### 1.1 Basemap of London

1. Go to the website  [ONS](https://geoportal.statistics.gov.uk/datasets/8edafbe3276d4b56aec60991cbddda50_2). The title should be:Local Authority Districts (December 2015) Generalised Clipped Boundaries in Great Britain.


2. Download the corresponding shapefile;

3. The right name of the file is 'Local_Authority_Districts__December_2015__Boundaries-shp.zip';

4. Unzip the data and save it.


### 1.2 Gender Participation Gap

1. Go to [London Datastore](https://data.london.gov.uk/dataset/earnings-workplace-borough);

2. Download 'earnings-workplace-borough.xls' and save it.


### 1.3 Gender Employment Gap

1. Go to [London Datastore](https://data.london.gov.uk/dataset/employment-gaps);

2. Navigate to 'employment gaps by gender and disability boroughs.xlsx' and download it, it is also the correct name. 


### 1.4 Gender Advancement Gap

1. Go to [London Datastore](https://data.london.gov.uk/dataset/employment-occupation-type-and-gender-borough);

2. Download file 'employment-by-occ-and-gender.xls'.


---

## 2. Load packages

There are all the packages needed for running this markdown file. To make things tidy, I choose to mute all the messages following this chunk.
```{r, message=FALSE}
library(sf)
library(tmap)
library(tmaptools)
library(tidyverse)
library(here)
library(readxl)
library(RSQLite)
library(dplyr)
library(ggplot2)
library(spdep)
```

---

## 3. Basemap


```{r}
#Read the shp file
Londonborough <- st_read('data/Local_Authority_Districts__December_2015__Boundaries-shp/Local_Authority_Districts__December_2015__Boundaries.shp')%>%
  filter(str_detect(lad15cd, "^E09"))%>%
  st_transform(., 27700)%>%
  rename(NAME = lad15nm)

tm0 <- qtm(Londonborough)

tmap_save(tm=tm0,filename = '0.basemap.png')

tm0
```

---


## 4. Gender Pay Gap

### 4.1 Calculation
```{r}
#Read the Gender Pay Gap file 
#Extract male data of Greater London
PayGap_Male <- read_excel("data/earnings-workplace-borough.xls", sheet = 2)%>% 
  .[c(2:34),c(2,45)]
#Extract female data of Greater London
PayGap_Female <- read_excel("data/earnings-workplace-borough.xls", sheet = 3)%>% 
  .[c(2:34),c(2,45)]

#For simply use, rename the columns
names(PayGap_Male) <- c('NAME','GPG_Male')
names(PayGap_Female) <- c('NAME','GPG_Female')

#In original data set, the mean value is not numeric
PayGap_Male$GPG_Male <- as.numeric(PayGap_Male$GPG_Male)
PayGap_Female$GPG_Female <- as.numeric(PayGap_Female$GPG_Female)

#Female value over male value
PayGap <- merge(PayGap_Male,PayGap_Female, by = 'NAME')
PayGap$GPG <- PayGap$GPG_Female/PayGap$GPG_Male
```

### 4.2 Plot Index
```{r}
#Collaborate two data sets
data1 <- merge(Londonborough, PayGap, by='NAME')

#Draw map
tmap_mode('plot') 

tm1 <- tm_shape(data1) + 
  tm_polygons(col = "GPG", 
              title = 'GPG',
              midpoint = NA,
              palette="RdPu",
              legend.hist=T)+
  tm_layout(legend.outside = TRUE)+
  tm_borders()+
  tm_compass()+
  tm_scale_bar()+
  tm_credits("(a)", position=c(0,0.85), size=1.5)


tmap_save(tm=tm1,filename = '1.GPG.png')

tm1
```


## 5. Employment Gap

### 5.1 Calculation
```{r}
#Import
EmpGap <- read_excel("data/employment gaps by gender and disability boroughs.xlsx", col_names = FALSE, skip = 46, sheet = '2018') %>% .[c(3:35),c(1,8,12)]

#Rename header
names(EmpGap) <- c('NAME','MaleEmploy','FemaleEmploy')

#In original data set, the value is not numeric
EmpGap$MaleEmploy <- as.numeric(EmpGap$MaleEmploy)
EmpGap$FemaleEmploy <- as.numeric(EmpGap$FemaleEmploy)

#Female value over male value
EmpGap$EG <- EmpGap$FemaleEmploy/EmpGap$MaleEmploy
```
### 5.2 Plot Index
```{r}
#Use the same GSS code to collaborate two data sets
data2 <- merge(Londonborough, EmpGap, by='NAME')

#Draw map
tmap_mode('plot') 

tm2 <- tm_shape(data2) + 
  tm_polygons(col = "EG",
              title = 'EG',
              midpoint = NA,
              palette="RdPu",
              legend.hist=T)+
  tm_layout(legend.outside = TRUE)+
  tm_borders()+
  tm_compass()+
  tm_scale_bar()+
  tm_credits("(b)", position=c(0,0.85), size=1.5)

tmap_save(tm=tm2,filename = '2.EG.png')
tm2
```

## 6. Advancement Gap

### 6.1 Calculation
```{r}
#Import file 
#Extract male data of Greater London
AdGap0 <- read_excel("data/employment-by-occ-and-gender.xlsx", sheet = '2018')%>% 
  .[c(3:35),c(2,5,9,13,41,45,49)]

#For simply use, rename the columns
names(AdGap0) <- c('NAME','Male1','Male2','Male3','Female1','Female2','Female3')

#In original data set, the mean value is not numeric
AdGap0$Male1 <- as.numeric(AdGap0$Male1)
AdGap0$Male2 <- as.numeric(AdGap0$Male2)
AdGap0$Male3 <- as.numeric(AdGap0$Male3)
AdGap0$Female1 <- as.numeric(AdGap0$Female1)
AdGap0$Female2 <- as.numeric(AdGap0$Female2)
AdGap0$Female3 <- as.numeric(AdGap0$Female3)

#update dataset
AdGap <- AdGap0[,1]
AdGap$Male <- AdGap0$Male1 + AdGap0$Male2 + AdGap0$Male3
AdGap$Female <- AdGap0$Female1 + AdGap0$Female2 + AdGap0$Female3

#Female value over male value
AdGap$AG <- AdGap$Female/AdGap$Male

```
### 6.2 Plot Index
```{r}
#Collaborate two data sets
data3 <- merge(Londonborough, AdGap, by='NAME')


#Draw map
tmap_mode('plot') 

tm3 <- tm_shape(data3) + 
  tm_polygons(col = "AG", 
              title = 'AG',
              midpoint = NA,
              palette="RdPu",
              legend.hist=T)+
  tm_layout(legend.outside = TRUE)+
  tm_borders()+
  tm_compass()+
  tm_scale_bar()+
  tm_credits("(c)", position=c(0,0.85), size=1.5)

tmap_save(tm=tm3,filename = '3.AG.png')

tm3
```

## 7. Economic Fairness Index
### 7.1 Calculation
```{r}
#merge data
index <- merge(PayGap, EmpGap, by='NAME') %>%
  merge(.,AdGap,by='NAME')

#If there is missing value, set it to be 0
index$GPG[is.na(index$GPG)] <- 0
index$EG[is.na(index$EG)] <- 0
index$AG[is.na(index$AG)] <- 0

#calculate standard deviation
#and change per 1% point
sdGPG <- sd(index$GPG)
per_sdGPG <- 0.01/sdGPG

sdEG <- sd(index$EG)
per_sdEG <- 0.01/sdEG

sdAG <- sd(index$AG, na.rm=TRUE)
per_sdAG <- 0.01/sdAG

SUM <- per_sdGPG + per_sdEG + per_sdAG

#Calculate the weight
weight_GPG <- per_sdGPG /SUM
weight_EG <- per_sdEG /SUM
weight_AG <- per_sdAG/SUM

#update original value
index$u_GPG <- weight_GPG * index$GPG
index$u_EG <- weight_EG * index$EG
index$u_AG <- weight_AG * index$AG

index$INDEX <- index$u_GPG + index$u_EG + index$u_AG
index$INDEX <- as.numeric(index$INDEX)
```


### 7.2 Plot Index
```{r}
#Use the same GSS code to collaborate two data sets
data4 <- merge(Londonborough, index, by='NAME')

tmap_mode('plot') 

tm4 <- tm_shape(data4) + 
  tm_polygons(col = "INDEX",
              title = 'EGFI',
              midpoint = NA,
              palette="RdPu",
              legend.hist=T)+
  tm_layout(legend.outside = TRUE)+
  tm_borders()+
  tm_compass()+
  tm_scale_bar()+
  tm_credits("(d)", position=c(0,0.85), size=1.5)

tmap_save(tm=tm4,filename = '4.index.png')

tm4
```

### 7.3 Plot together
```{r,message=FALSE}
t = tmap_arrange(tm1,tm2,tm3,tm4)
tmap_save(tm=t,filename = '5.all.png')

t
```

### 7.4. Rank Line Graph
```{r}
data6 <- index[,c(1,4,7,10,14)]


data6$GPG_rank <- rank(data6$GPG)
data6$EG_rank <- rank(data6$EG)
data6$AG_rank <- rank(data6$AG)
data6$INDEX_rank <- rank(data6$INDEX)

rank1 <- cbind(data6$NAME,data6$GPG_rank,'1.GPG')
rank2 <- cbind(data6$NAME,data6$EG_rank,'2.EG')
rank3 <- cbind(data6$NAME,data6$AG_rank,'3.AG')
rank4 <- cbind(data6$NAME,data6$INDEX_rank,'4.INDEX')

rank <- as.data.frame(rbind(rank1,rank2,rank3,rank4))
names(rank) <- c('Borough','Rank','Type')

rank[,2] <- as.numeric(rank[,2])


linegraph<-
  ggplot(rank, aes(x= Type, y = Rank, group=Borough))+
  geom_line(aes(color=Borough))+
  theme(legend.position="bottom",
        legend.text = element_text(size = 5),
        legend.title = element_text(size= 7))
ggsave('6.linegraph.png')

linegraph
```


## 8. Spatial analysis

```{r}
#Use the data containing INDEX and Geographic Information
data5 <- data4

#Check NA values
which(is.na(data5$GPG),arr.ind = TRUE)
which(is.na(data5$EG),arr.ind = TRUE)
which(is.na(data5$AG),arr.ind = TRUE)
which(is.na(data5$INDEX),arr.ind = TRUE)
```


```{r}
#Find centroids of each borough
data5_cen <- st_geometry(st_centroid(data5))

#Neighbour
data5_nb <- poly2nb(data5, queen=T)

#Add centroids and Neighbor together to check
plot(data5_nb, data5_cen, col="red")
plot(data5$geometry, add = T)
```


```{r}
#Weight
data5.weight <- nb2listw(data5_nb, style="W")

#Moran Test
moran.test(data5$INDEX, data5.weight)
#Find confidence interval
z1 <- qnorm(0.1645/2,lower.tail = FALSE)
0.06931420 + z1 * sqrt(0.01061529)
0.06931420 - z1 * sqrt(0.01061529)

#Geary’s C Test
geary.test(data5$INDEX, data5.weight)
#Find confidence interval
z2 <- qnorm(0.1773/2, lower.tail = FALSE)
0.90303349 + z2 * sqrt(0.01097463)
0.90303349 - z2 * sqrt(0.01097463)
```








